%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Dhirendra Pratap}{Singh}{ \urlstyle{same}\href{http://singhdhirendrafolio.blogspot.com}{singhdhirendrafolio.blogspot.com}| \href{https://www.linkedin.com/in/hanisntsolo}{linkedin.com/hanisntsolo}\\
\href{mailto:ds.pratap1997@gmail.com}{ds.pratap1997@gmail.com} | 916.976.1452 | \href{mailto:ds.pratap1997@bbdnitm.ac.in}{ds.pratap1997@bbdnitm.ac.in}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical Skills/Programming}
\location{Over 5000 lines:}
JavaScript \textbullet{}   TACL \textbullet{} Python \textbullet{} Java \\
Shell \textbullet{} ReactJS \textbullet{} Microsoft Flow \\ 
\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} CSS  \textbullet{} HTML \\
\location{Familiar:}
PostgreSQL \textbullet{} GCP \textbullet{} OCI \textbullet{} MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Dr. APJ Abdul Kalam Technical University}
\descript{BTech in Electronics \& Comm.}
\location{Sep 2020 | Lucknow,India}
\sectionsep

% \subsection{Cornell University}
% \descript{BS in Computer Science}
\location{College of Engineering}
Babu Banarsi Das National\\ Institute Of Technology \& Management\\
\location{ Cum Laude. CGPA: 8.62 / 10.0}
\sectionsep

\subsection{Central Academy Schools}
\location{Grad. May 2015|  Lucknow, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://www.facebook.com/dhirendra1997/}{\bf singhDhirendra} \\
Github:// \href{https://github.com/hanisntsolo}{\bf hanisntsolo} \\
LinkedIn://  \href{https://www.linkedin.com/in/hanisntsolo/}{\bf hanisntsolo} \\
YouTube://  \href{https://www.youtube.com/channel/UCudY5NQeinXTD9I6eVn1WeQ}{\bf tech | info | geek} \\
Twitter://  \href{https://twitter.com/_dhirendra}{\bf @\_dhirendra} \\
Pinterest://  \href{https://in.pinterest.com/hanisntoslo/boards/}{\bf haninstsolo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Embedded Systems Design \\
Object Oriented Programming \\
Cloud Computing \\
Machine Learning \\
Open Source Software Engineering \\
Advanced Interactive Graphics \\
Assembler + Practicum \\
Evolutionary Computation \\
Smart India Hackathon \\
{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
\sectionsep

\subsection{Undergraduate}
Information Retrieval \\
Operating Systems \\
Artificial Intelligence + Practicum \\
Functional Programming \\
Unix Tools and Scripting \\



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{Citi}
\descript{| Full Stack Developer (Assistant Manager) }
\location{July 2022 – Present | Pune, Maharashtra India}
\vspace{\topsep} % Fix for extra vertical space
\begin{tightemize}
\item Spearheaded integration efforts in Trade Commercial E-loans, driving \textbf{digital adoption by customers} and contributing to business growth.
\item Orchestrated migration of classic VMs to cloud infrastructure, reducing up-time costs through automated scaling and load-based billing.
\item Pioneered a customer-focused approach by developing a \textbf{Troubleshooting Automation Tool from scratch.} Leveraged React, Node, and Java as Micro-service to streamline customer issue resolution, significantly enhancing their experience.
\item Managed the end-to-end life-cycle of the Troubleshooting Automation Tool, including creation, migration, and deployment. Independently utilized Light-speed and other CI/CD [Teamcity and UrbanCodeDeploy] tools to ensure seamless implementation.
\item \textbf{Recognized for innovation and efficiency}, registered the Troubleshooting Automation Tool as an internal product, available for use by internal employees. This initiative further contributed to improving the overall internal processes.
\end{tightemize}
\sectionsep

\runsubsection{Capgemini}
\descript{| Senior Software Engineer }
\location{Sep 2020 - Jun 2022 | Pune, Maharashtra, India}
% \vspace{\topsep} % Fix for extra vertical space
\begin{tightemize}
\item \textbf{{\href{https://singhdhirendrafolio.blogspot.com/2022/05/pulse-ams-l15-success-story-in-d-life.html}{Developed Scalable Incident Processor for Discover Financial Services, auto-closing 98\% incidents, cutting dwell time to net zero.}}} 
\item Enhanced data structures in non-native language TACL, boosting efficiency.
\item Automated tasks via Microsoft Flow, streamlining monitoring processes.
\item Full-stack developer: Code contributions in ReactJS, Java (Spring-Boot), and PostgreSQL.
\item Employed CI/CD tools (Git, SonarQube, Jenkins) with TDD approach within Agile framework.Rigorously tested rest controller using JUnit5 framework.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://www.suvasaa.com/}{SUVASAA}}
\descript{| Remote Software Engineering Intern }
\location{May 2020 – Aug 2020 | Atlanta, GA, USA}
\begin{tightemize}
\item Full stack dev for suvasaa-an e-commerce store: ReactJS, Firestore \& Firebase.
\item Segregated customer/admin login routes, added admin inventory interface.
\item Integrated online payments via Stripe API.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{\href{https://drive.google.com/file/d/1ySGyZqVcvsJw7d4tcCqRhxM72iqBXmRh/view?usp=sharing}{Water Pollution Monitoring}}
\descript{| Researcher}
\location{Sep 2019 – Feb 2020 | Lucknow, Uttar Pradesh India}
Worked with \textbf{\href{https://www.youtube.com/c/KalyanKrishnaAwasthi}{Prof KK Awasthi}} and \textbf{\href{https://www.linkedin.com/in/dr-shailendra-tahilyani-034bb27/}{Prof Shailendra Tahilyani}} to create \textbf{\href{https://www.youtube.com/watch?v=ZhUoPz8hMEY}{Poll-m-Boat}}, an embedded tool which  collects the extent of pollution in water bodies/ liquid environments.
\sectionsep

% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
% \location{Mar 2012 – May 2013 | Ithaca, NY}
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. 
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Facts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Fun facts}
\runsubsection{Intrests}
Entrepreneurship\textbullet{} Investing \textbullet{} Mentoring\\
\vspace{\topsep}
\runsubsection{Hobbies} 
Lifting \textbullet{} Reading \textbullet{} Cycling \textbullet{} Running \textbullet{} Swimming\\
\vspace{\topsep}
\runsubsection{Volunteer Experience} 
\vspace{\topsep}
Old Age Home \textbullet{}\textbf{\href{https://www.helpageindia.org/}{ @Astha Foundation}}\\
\runsubsection{WINGMAN} 
(Academic Support Volunteer) \textbullet{}\textbf{\href{https://makeadiff.in//}{ @Make A Difference}}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
