%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{dhirendra-pratap-singh-resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Dhirendra Pratap}{Singh}{ \urlstyle{same}\href{http://hanisntsolo.github.io}{hanisntsolo.com} | \href{https://www.linkedin.com/in/hanisntsolo}{linkedin} | \href{https://github.com/hanisntsolo}{github} \\
\href{mailto:ds.pratap1997@gmail.com}{ds.pratap1997@gmail.com} | \href{tel:+919169761452} {916.976.1452} | \href{mailto:ds.pratap1997@bbdnitm.ac.in}{ds.pratap1997@bbdnitm.ac.in}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
{\subsection{Private Cloud}}
\href{https://dozzle.hanisntsolo.com}{\location{With 32+ Services and Adv. Tooling}}
Docker \textbullet{} Nginx \textbullet{} CI/CD
\subsection{Languages}
\location{Over 5000: lines}
Java \textbullet{} Python \textbullet{} TypeScript \\
JavaScript \textbullet{} C \textbullet{} C++ \textbullet{} HTML \textbullet{} CSS

\subsection{Frameworks}
\location{Over 2000: lines}
ReactJS \textbullet{} Spring Boot \\
Node.js \textbullet{} Shell Scripting

\subsection{Tools/Platforms}
GCP \textbullet{} OCI \textbullet{} Microsoft Flow \\
PostgreSQL \textbullet{} MySQL \textbullet{} Git \textbullet{} Jenkins
\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Dr. APJ Abdul Kalam Technical University}
\descript{BTech in Electronics \& Communication}
\location{Sep 2020 | Lucknow, India}
Babu Banarsi Das National Institute of Technology \& Management\\
\location{CGPA: 8.62 / 10.0}
\sectionsep

\subsection{Central Academy \\ Schools}
\location{Grad. May 2015 | Lucknow, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/hanisntsolo}{\bf hanisntsolo} \\
LinkedIn://  \href{https://www.linkedin.com/in/hanisntsolo/}{\bf hanisntsolo} \\
YouTube://  \href{https://www.youtube.com/channel/UCudY5NQeinXTD9I6eVn1WeQ}{\bf tech | info | geek} \\
Twitter://  \href{https://twitter.com/_dhirendra}{\bf @\_dhirendra} \\
Pinterest://  \href{https://in.pinterest.com/hanisntoslo/boards/}{\bf hanisntsolo}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Cloud Computing \\
Machine Learning \\
Open Source Software Engineering \\
Embedded Systems Design \\
Object-Oriented Programming \\
Evolutionary Computation

\subsection{Undergraduate}
Operating Systems \\
Artificial Intelligence + Practicum \\
Unix Tools and Scripting \\
Information Retrieval
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{Citi}
\descript{| Full Stack Developer (Assistant Manager) }
\location{July 2022 – Present | Pune, Maharashtra, India}
\vspace{\topsep}
\begin{tightemize}
\item Spearheaded integration efforts in Trade Commercial E-loans, driving \textbf{digital adoption by customers}, contributing to business growth.
\item Migrated classic VMs to cloud infrastructure, reducing up-time costs through \textbf{automated scaling} and load-based billing.
\item Developed a \textbf{Troubleshooting Automation Tool} from scratch using React, Node, and Java microservices, streamlining client issue resolution.
\item Independently handled end-to-end lifecycle (creation, migration, deployment) of the tool, ensuring seamless implementation using CI/CD tools.
\item Registered the tool as an internal product, enabling usage by internal employees and improving internal processes.
\end{tightemize}
% \sectionsep

\runsubsection{Capgemini}
\descript{| Senior Software Engineer }
\location{Sep 2020 – Jun 2022 | Pune, Maharashtra, India}
% \vspace{\topsep}
\begin{tightemize}
\item Developed a scalable incident processor(800 lines TACL)for Discover Financial Services, \textbf{auto-closing 98\% of incidents}, cutting dwell time to net zero.
% \item Enhanced data structures in TACL, improving processing efficiency.
% \item Automated tasks using Microsoft Flow, streamlining monitoring.
\item Full-stack contributions in ReactJS, Spring Boot, and PostgreSQL.
% \item Employed CI/CD tools and TDD approach within Agile framework. Rigorously tested rest controller using JUnit5.
\end{tightemize}
% \sectionsep

\runsubsection{SUVASAA}
\descript{| Remote Software Engineering Intern }
\location{May 2020 – Aug 2020 | Atlanta, GA, USA}
\begin{tightemize}
\item Full-stack development of an e-commerce platform using ReactJS and Firebase.
\item Integrated online payments via Stripe API and managed segregated customer/admin routes.
\end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\href{https://faangcracker.hanisntsolo.com/}{\runsubsection{FAANG-CRACKER}}
\descript{| \href{https://faangcracker.hanisntsolo.com/}{Coding Tool (In Progress)} | \href{https://faangcracker.hanisntsolo.com/}{Check it out!} }
\begin{tightemize}
\item Developing a tool to automate FAANG interview prep, integrating Codeforces and LeetCode APIs. Built with Next.js, Node.js, and WebSocket support for code compilation in Java, Python, C++, and JavaScript.
\end{tightemize}

\href{https://github.com/hanisntsolo/resume}{\runsubsection{GitHub Resume` Project}}
\descript{| \href{https://github.com/hanisntsolo/resume}{View on GitHub} | \href{https://resume.hanisntsolo.com/}{View my Resume`}}
\begin{tightemize}
\item Created a resume template in LaTeX with automated deployment via GitHub Workflows. Allows users to fork and deploy their resume publicly in just a few steps.
\end{tightemize}

\href{https://github.com/hanisntsolo/codeforces-lamp}{\runsubsection{Codeforces Lamp}}
\descript{| \href{https://github.com/hanisntsolo/codeforces-lamp}{View on GitHub} }
\begin{tightemize}
\item Built an automated tool that changes colors based on Codeforces submissions using the Tuya API. Developed with Python and Flask, deployed via Docker, and customizable through environment variables for public use.
\end{tightemize}

\href{https://github.com/hanisntsolo/auto-committer}{\runsubsection{Auto-committer}}
\descript{| \href{https://github.com/hanisntsolo/auto-committer}{View on GitHub} }
\begin{tightemize}
\item Automated repository management tool that commits frequent file changes from private cloud environments or JupyterLab to ensure real-time backup via Docker and Python.
\end{tightemize}


% Very big section - 
% \section{Projects}

% \runsubsection{Codeforces Lamp}
% \descript{| \href{https://github.com/hanisntsolo/codeforces-lamp}{View on GitHub} }
% Developed an innovative automation tool that changes colors based on a user’s Codeforces submission status. Integrated with the Tuya API using Python and Flask, and deployed as a Dockerized service for public use. Users can easily customize the setup by configuring environment variables, allowing anyone to visualize their competitive programming progress in real time.

% \runsubsection{Auto-committer}
% \descript{| \href{https://github.com/hanisntsolo/auto-committer}{View on GitHub} }
% Automated repository management solution designed for frequent file changes, particularly on private cloud platforms or JupyterLab environments. This tool tracks modifications and automatically commits them to the repository, preventing data loss and ensuring all files are consistently backed up in real time.

% \runsubsection{GitHub Resume Project}
% \descript{| \href{https://github.com/hanisntsolo/resume}{View on GitHub} | \href{https://resume.hanisntsolo.com/}{View my Resume} }
% Created a streamlined, modern resume template using LaTeX, aimed at professionals who want to automate resume deployment. The project integrates with GitHub Workflows to automatically deploy the resume to a public endpoint. Users can fork the repository to build and maintain their own public resume in just a few steps.

% \runsubsection{FAANG-CRACKER}
% \descript{| Coding Tool (In Progress) | \href{https://faangcracker.hanisntsolo.com/}{Check it out!} }
% Building a custom tool designed to help engineers prepare for FAANG interviews by automating problem-solving workflows. It integrates with Codeforces and LeetCode APIs to pull problems and track user performance. Built using Next.js and Node.js with WebSocket support for real-time code compilation. The tool currently supports Java, Python, C++, and JavaScript, offering a personalized and streamlined interview preparation experience.

% \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     FUN FACTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Fun facts}
\runsubsection{Interests}
Entrepreneurship \textbullet{} Investing \textbullet{} Mentoring

\runsubsection{Hobbies}
Lifting \textbullet{} Reading \textbullet{} Cycling \textbullet{} Swimming

\runsubsection{Volunteer Experience}
Old Age Home \textbullet{} \href{https://www.helpageindia.org/}{@Astha Foundation} \\
\runsubsection{WINGMAN} (Academic Support Volunteer) \textbullet{} \href{https://makeadiff.in}{@Make A Difference}
% \sectionsep
\end{minipage}
\end{document}
